Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-25 texor.Rmd
partially completed the processing of legacy articles section

# Known problems needing manual fixes

>>>>

The R Journal has been operating since 2009, and has published 682 articles through 2022 in addition to numerous editorials and news items. These LaTeX articles are the main focus of the conversions made with \CRANpkg{texor} and \CRANpkg{rebib}.

## Batch processing

The code is designed to process an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument.  The vignette [Introduction to texor](https://abhi-1u.github.io/texor/articles/introduction-to-texor.html) provides more details.

## Known problems requiring manual fixes

## Plan for release

The HTML versions of all successfully converted legacy articles will be on the [R Journal web site](https://journal.r-project.org) late in 2023. The final step in the integration requires the R Markdown file to be knitted in place to capture the meta data for each article.

## Reporting problems

As a consequence of this project, the journal web site has been furnished with an additional link titled "CONTRIBUTE". Visiting this link will give you details on how to report a problem with an article that you are readin, or even to make a suggestion on improving operations.

### 2023-08-25 texor.tex
partially completed the processing of legacy articles section

\hypertarget{known-problems-needing-manual-fixes}{%
\section{Known problems needing manual fixes}\label{known-problems-needing-manual-fixes}}

>>>>

The R Journal has been operating since 2009, and has published 682 articles through 2022 in addition to numerous editorials and news items. These LaTeX articles are the main focus of the conversions made with \CRANpkg{texor} and \CRANpkg{rebib}.

\hypertarget{batch-processing}{%
\subsection{Batch processing}\label{batch-processing}}

The code is designed to process an issue at a time, by operating on all the files in the directory housing the issue. Each processing function, from pre-processing the text in the LaTeX file to post-processing accepts a directory name as the argument. The vignette \href{https://abhi-1u.github.io/texor/articles/introduction-to-texor.html}{Introduction to texor} provides more details.

\hypertarget{known-problems-requiring-manual-fixes}{%
\subsection{Known problems requiring manual fixes}\label{known-problems-requiring-manual-fixes}}

\hypertarget{plan-for-release}{%
\subsection{Plan for release}\label{plan-for-release}}

The HTML versions of all successfully converted legacy articles will be on the \href{https://journal.r-project.org}{R Journal web site} late in 2023. The final step in the integration requires the R Markdown file to be knitted in place to capture the meta data for each article.

\hypertarget{reporting-problems}{%
\subsection{Reporting problems}\label{reporting-problems}}

As a consequence of this project, the journal web site has been furnished with an additional link titled ``CONTRIBUTE''. Visiting this link will give you details on how to report a problem with an article that you are readin, or even to make a suggestion on improving operations.
